\documentclass[margin,line,pifont,palatino,courier]{res}

\usepackage{pifont}
\usepackage{hyperref}
\usepackage[latin1] { inputenc}
\textheight=9.0in
\addtolength{\topmargin}{-0.5in}


\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
\rfoot{ {\footnotesize Curriculum Vitae, Matthew Cadier Kim, \thepage} }


\newenvironment{list1}{
  \begin{list}{\label{ } }{
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.0in} } }{\end{list} }
\newenvironment{list2}{
  \begin{list}{$\bullet$}{
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in} } }{\end{list} }

\begin{document}

\name{Matthew Cadier Kim \vspace*{.1in} }


\begin{resume}


%%%%%%%%%    Contact information   %%%%%%%%%%%


\begin{flushright}
{\small
San Francisco CA \\
1 (415) 767-8984\\
% \url{thecity.sfsu.edu/~mcadier} \\
  \verb+m.cadier.kim@gmail.com+
}
\end{flushright}
 
\section{\sc  About Me}
    
      
          
      
          
            Machine learning engineer and applied mathematician.  Building real-time inference and prediction 
systems for payments fraud, on-demand logistics, and platform security.  Built machine vision pipelines 
and classifiers for epidemiology and did research in combinatorial optimization and discrete geometry.
          
      
          
      
          
      
          
      


\section{\sc  Work History}
  
  
    \employer{ Coinbase }
    \title{ Machine Learning Engineer  }
    \location{  San Francisco, CA   }
    \dates{ November 2017 - present }

    \begin{position}
    Backend services delivering model predictions and rule evaluations for payments risk, event pipelines, ETL, data warehousing.
    \end{position}
  
    \employer{ Postmates }
    \title{ Data Scientist  }
    \location{  San Francisco, CA   }
    \dates{ May, 2016 - November 2017 }

    \begin{position}
    Built event-based prediction services for payments fraud, platform abuse, and prep-time estimation.  Worked on systems to train and deploy statistical models, internal services and apis, airflow maintance, ETL jobs, ad hoc analysis, BI table design, and running portions of the interviews for DS and DE candidates.
    \end{position}
  
    \employer{ UCSF Proctor Foundation }
    \title{ Machine Vision Engineer   }
    \location{  San Francisco, CA   }
    \dates{ May, 2015 - present }

    \begin{position}
    Worked on a grant funded project to detect Trachoma in field images. I investigated and developed machine learning algorithms to classify images of eyelids. I worked with the PI to define the direction of the project and was the principal developer of the grading application.
    \end{position}
  
    \employer{ Argyle Data }
    \title{ Data Scientist  }
    \location{  San Mateo, CA   }
    \dates{ June, 2014 - February, 2015 }

    \begin{position}
    I prototyped statistical machine learning algorithms for time series analysis and fraud detection in network data as well as implemented production versions in Java.
    \end{position}
  

\section{\sc Languages/ \\ Tools}

  \begin{tabular}{@{}p{6in}p{3in}}

     Python,  Ruby,  Java,  SQL dialects 
    \\working with: \ 
     Django, Rails, Flask,  Redshift,  Scikit-learn,  General AWS services 

  \end{tabular}


\section{\sc Papers}
  \begin{tabular}{@{}p{5in}}
    \begin{list1}
      
      
        
            \item {\em A Characterization of Generalized Permutohedra for the Classical Reflection Groups},  2015, (thesis)  
        
      \vspace{.2em}
      
        
      \vspace{.2em}
      
        
      \vspace{.2em}
      
        
            \item {\em Sensitivity and specificity of computer vision classification of eyelid photographs for programmatic trachoma assessment},  with Dr. Travis Porco and Dr. Kazunori Okada,  2015, (UCSF F. I. Proctor Foundation project)  
        
      \vspace{.2em}
      
        
            \item {\em Free resoltuions of matroid ideals},  with Justin Davis,  2015 
        
      \vspace{.2em}
      
    \end{list1}
  \end{tabular}


\section{\sc Education} 
  %\vspace*{-.1in}
  \begin{list1}
    
    
        \item  {\bf SFSU:}\textbf{ MA }, Mathematics, 2016

          
    
        \item  {\bf University of Paris-1:}\textbf{ Visiting Student }, Philosophy, Logic, Mathematics, 2009-2011

          
    
        \item  {\bf SFSU:}\textbf{ BA }, Philosophy, Mathematics, Computer Science, 2012

          
    

  \end{list1}



\end{resume}



\end{document}

