% Cover letter using letter.cls
\documentclass[11pt]{letter} % default is 10 pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font 
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page
\textheight=8.5in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}


\signature{Matthew Kim}                  % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
\begin{letter}{Yelp.com Data-Mining Engineer Internship Application\\
 Cover Letter} 

\begin{center}
\bf Matthew Kim\\
2137 Alemany Blvd\\ San Francisco, CA 94112\\ (949) 436-1220
\end{center} 
\vfill % forces letterhead to top of page

\opening{} 

It is refreshing to to see that the Yelp online application is so simple and accepts cover letters and LinkedIn profiles, rather than the usual high-volume online application forms.  While still unsure about how this process works, and whether my CV will make it past the first rounds of keyword scans, I hope that if this letter is read, it will justify my qualification as a {\bf data-mining intern}
  So I'd like to supplement my CV here, somewhat anecdotally, with reasons why I should be considered. 
  
I will be the first to admit that my background, on paper, is not the most impressive when it comes to programming and information technology experience; these are topics that I have had to explore largely outside of academics.  The first part of my academic career was oriented towards the social sciences. However after rediscovering a passion for the quantitative, I completed the curriculum for the undergraduate program in mathematics over the past two semesters, and will be working on a MA this coming fall. Despite the late entry, I quickly established myself as "the-guy-you-go-to-for-help," for most of the undergraduate material.  Despite this accelerated initiation, I still have much to learn obviously.   Hence the solicitation for internships.  But I think that this demonstrates a proven ability to learn new technical and conceptual material quickly through self-motivation and a capacity to create navigable paths through information.  

Currently, I am conducting rather informal research on Wavelets, data compression, and signal processing through the NSF grant of one of my professors.  However, my other primary interests going into the MA will be statistical data analysis and algebraic statistics.  As mentioned in my CV, I have academic experience in statistics and in categorical data analysis as well as programming in object oriented languages and R, and data set manipulation with R and MS excel.   Having said that, the more I self study, the more I realize how little I know, so I am not going to play up my relatively meager knowledge.  What I do know however, is that given most practical problems involving at least one small aspect of my current expertise, I have great confidence in my scientific, theoretic, historical, interpersonal, and geopolitical resourcefulness to be able to solve the problem or execute the project 






   \closing{Sincerely,}
   Matthew Kim
 


\end{letter}
 

\end{document}