\documentclass[margin,line,pifont,palatino,courier]{res}

\usepackage{pifont}
\usepackage{hyperref}
\usepackage[latin1] { inputenc}
\textheight=9.0in
\addtolength{\topmargin}{-0.5in}


\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
\rfoot{{\footnotesize Curriculum Vitae, Matthew Cadier Kim, \thepage}}


\newenvironment{list1}{
  \begin{list}{\label{}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.0in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{Matthew Cadier Kim \vspace*{.1in}}


\begin{resume}


%%%%%%%%%    Contact information   %%%%%%%%%%%


\begin{flushright}
{\small
Thorton Hall 912, 1600 Holloway Ave, San Francisco, CA 94132. \\
+1 (415) 767-8984\\
% \url{thecity.sfsu.edu/~mcadier} \\
  \verb+m.cadier.kim@gmail.com+
}
\end{flushright}
 
\section{\sc  About Me}
\input{../content/about.txt}



 \section{\sc Education} 
%\vspace*{-.1in}
\begin{list1}
\item  {\bf SFSU:}  \textbf{M.A.} ~ in Mathematics, 2015 (in progress) \\
Advisor: Dr. Federico Ardila. \\
 Thesis: {\em The Geometry of Generalized $W$ Permutohedra} 


\item  {\bf SFSU:}  \textbf{B.A.} ~ Mathematics, Philosophy, Computer Science, May 2012 

\end{list1}





 \section{\sc Awards}
\begin{list1}
  \item  Maxwell Scholarship, College of Science and Engineering, SFSU, \$4,000,  2013-14.
  \item $(CM)^2$ grant, Department of Mathematics, SFSU, \$5,000, 2012-2013.
\end{list1}






%  \section{\sc Talks}
% \begin{list1}
%     \item  Encuentro Colombiano de Combinatoria, Bogot\'a Colombia, 
%      {\em Generalized Permutohedra and Signed Permutohedra}, 2014. 
% \end{list1}




%%%%%%%%%%%%%%%%%%   Papers %%%%%%%%%%%%%%%%%%%%%%%



\section{\sc Papers}
\begin{tabular}{@{}p{5in}}
    {\em A Neural Network Architecture for Detecting Trachoma Infection} with Dr. Travis Porco (UCSF) and Dr. Kazunori Okada. \\

    {\em A Characterization of Generalized Permutohedra of the Classical Reflection Groups} with David Arcila and Juli\'an Romero, 2015
\end{tabular}








%%%%%%%%%%%%%%%%%%   Industry  %%%%%%%%%%%%%%%%%%%%%%%

\section{\sc  Work History}

\employer{UCSF: UCSF The Francis I. Proctor Foundation}
\title{Visiting Researcher}
\location{San Francisco, CA}
\dates{May, 2015 - December 2015}

\begin{position}
Research and develop a novel artificial vision algorithm to detect the presence of follicles on images of everted eyelids using a convolutional neural networks.  Additionally I work on an image processing pipeline to label, segment and preprocess the images coming from the field. 
\end{position}

\employer{Argyle Data}
 \title{Data Science Associate} 
 \location{San Mateo, CA}
 \dates{June, 2014 - February, 2015}

\begin{position}
I worked alongside the senior software engineer to research, prototype, and develop machine learning and statistical algorithms for fraud detection.
\end{position}


\employer{SFSU}
 \title{Graduate Teaching Assistant} 
 \location{San Francisco, CA}
 \dates{September 2012 - December 2014}

\begin{position}
Taught undergraduate algebra, precalculus and calculus courses. 
\end{position}




\section{\sc  Selected Projects}

\begin{list2}
  \item Researching, implementing, and testing hidden Markov models for fraud detection in a telecommunications network. This involved extensive exploration, querying, and munging of network packet data. 

  \item Adapted and implemented a counting Bloom filter design from an AT\&T research paper for Spam detection in SMS traffic.   

  \item Investigating the applicability of a recurrent neural network classifier for use on a set of medical images gathered by researchers at the Francis I Proctor Foundation at UCSF. ( in progress)
\end{list2}



\section{\sc Programming\\ Languages}

\begin{tabular}{@{}p{6in}p{3in}}

Java, Python, Matlab, Julia,  C/C++, Ruby, Latex \\


\end{tabular}


\section{\sc  Languages}
  English (Native), French (Fluent written and oral)


\section{\sc   References}

\begin{list1}
\item {\bf Arshak Navruzyan}, VP of Product Management, Argyle Data, \\
 \texttt{arshak.navruzyan@argyledata.com}

\item {\bf Dejan Miljkovic}  Senior Software Engineer, Argyle Data,\\
 \texttt{dejan.miljkovic@argyledata.com} 
 
\end{list1}


\end{resume}



\end{document}

