\documentclass[margin,line,pifont,palatino,courier]{res}

\usepackage{pifont}
\usepackage{hyperref}
\usepackage[latin1] { inputenc}
\textheight=9.0in
\addtolength{\topmargin}{-0.5in}


\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhf{}
\rfoot{{\footnotesize Curriculum Vitae, Matthew Cadier Kim, \thepage}}


\newenvironment{list1}{
  \begin{list}{\label{}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.0in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{Matthew Cadier Kim \vspace*{.1in}}


\begin{resume}
\begin{flushright}
{\small
Thorton Hall 912, 1600 Holloway Ave, San Francisco, CA 94132. \\
% \url{thecity.sfsu.edu/~mcadier} \\
  \verb+m.cadier.kim@gmail.com+
}
\end{flushright}
 



 \section{\sc Education} 
%\vspace*{-.1in}
\begin{list1}
\item  {\bf SFSU:}  \textbf{M.A.} ~ in Mathematics, 2015 (in progress) \\
Advisor: Dr. Federico Ardila. \\
 Thesis: {\em The Geometry of Signed Generalized Permutohedra} 


\item  {\bf SFSU:}  \textbf{B.A.}~in Philosophy, minor:    
Mathematics, May 2012 

\item {\bf Universti\'e Paris 1 Panth\'{e}on-Sorbonne}

CSU International Exchange program in the dept. of Logic. 2010-2011\\

%\item {\bf University of Paris 8 Saint-Denis} 
%
%CSU International Program participant 2009-2010\\

\end{list1}





 \section{\sc Awards}
\begin{list1}
  \item  Maxwell Scholarship, College of Science and Engineering, SFSU, \$4,000,  2013-14.
  \item $(CM)^2$ grant, Department of Mathematics, SFSU, \$5,000, 2012-2013.
\end{list1}






%  \section{\sc Talks}
% \begin{list1}
%     \item  Encuentro Colombiano de Combinatoria, Bogot\'a Colombia, 
%      {\em Generalized Permutohedra and Signed Permutohedra}, 2014. 
% \end{list1}




%%%%%%%%%%%%%%%%%%   Papers %%%%%%%%%%%%%%%%%%%%%%%



\section{\sc Papers}
\begin{tabular}{@{}p{5in}}
    {\em Signed Permutohedra} with David Arcila and Juli\'an Romero, 2013
\end{tabular}



%%%%%%%%%%%%%%%%%%   CONFERENCES %%%%%%%%%%%%%%%%%%%%%%%



\section{\sc Conferences Attended}
\begin{list1}
\item Symbolic and Numerical Methods for Tensors and Representation Theory, Simons Institute, Berkeley , USA, 2014.
\item  Stanley @70, MIT, Cambridge, USA, 2014.
\item Encuentro Colombiano de Combinatoria, Univsersidad de Los Andes, Bogot\'a, Colombia, 2014.
\item Bay Area Discrete Math Day, Santa Clara, 2014
\item  Bay Area Discrete Math Day, Berkeley, USA, 2013.
\end{list1}




%%%%%%%%%%%%%%%%%%   TEACHING  %%%%%%%%%%%%%%%%%%%%%%%


\section{\sc  Teaching}
\begin{list1}
\item Pre-calculus Supplemental Class: \ Fall 2014, Spring 2014
\item  TA Calculus I and II: \ Spring 2013, Fall 2013, Spring 2013
\item Algebra II: \ Spring 2013, Summer 2013
\item Algebra I: \ Fall 2013
\end{list1}


% \begin{tabular}{@{}p{1in}p{3in}}
% Fall 2014 &   Pre-calculus Supplemental Class \\
% Spring 2014 &  TA Calculus I and II \\
% Spring 2014 &  Pre-calculus Supplemental Class \\
% Fall 2013 &  TA Calculus I and II \\
% Summer 2013 & Algebra II \\
% Spring 2013 &  Algebra II \\
% Spring 2013 &  TA Calculus I and II \\
% Fall 2012 &  Algebra I (2 sections) \\
% \end{tabular}


%%%%%%%%%%%%%%%%%%   Industry  %%%%%%%%%%%%%%%%%%%%%%%

\section{\sc  Work History}

\begin{list1}
 \item Argyle Data, Data Science Associate, 2014 - present.
 \item SFSU, Graduate Teaching Assistant, September 2012 - December 2014.
\end{list1}



\section{\sc  Selected Projects}



\section{\sc Programming\\ Languages}

\begin{tabular}{@{}p{6in}p{3in}}

Java, Python, Matlab, Julia,  C/C++, Ruby, Latex \\


\end{tabular}



\section{\sc  Languages}
  English (Native), French (Fluent written and oral)


\section{\sc   References}

\begin{list1}
\item {\bf Federico Ardila}, Associate Professor of Mathematics, SFSU, \texttt{federico@sfsu.edu}

\item {\bf Dr. Serkan Hosten}  Professor of Mathematics, SFSU, \texttt{serkan@sfsu.edu} 

\item {\bf Dr. Joseph Gubeladze},  Professor of Mathematics,  SFSU, \texttt{soso@sfsu.edu} 
\end{list1}


\end{resume}



\end{document}

